### 2019-04-21 sections/esti/esti_one.tex
overleaf zotero sync again

Besides the age at school closure, the impact of school closure on educational attainment may also differ by the number of years of exposure to the policy: short-run effects of closure on a child's educational attainment progression could be dampened or amplified over the medium and long run.\footnote{After an individual completes schooling, duration effects will become constant. In studies with cross-sectional data taken long after a policy has been implemented, \textcite{duflo_2001_school} for example, the duration effect is irrelevant because all educational attainment data is observed long after sample individuals have completed schooling. In our data, a significant proportion of individuals have not completed schooling, allowing us to have meaningful duration effects.}  In order to identify both age and duration effects with our cross-sectional data, we exploit the variation in the year of school closure. Under the assumption that the impact of the policy is not specific to the calendar year of closure, we can estimate Equation \ref{eq:startsLengths} to obtain the impact of the policy as a function of both starting age and the length of exposure.

>>>>

Besides the age at school closure, the impact of school closure on educational attainment may also differ by the number of years of exposure to the policy: short-run effects of closure on a child's educational attainment progression could be dampened or amplified over the medium and long run.\footnote{After an individual completes schooling, duration effects will become constant. In studies with cross-sectional data taken long after a policy has been implemented, \textcite{duflo_school_2001} for example, the duration effect is irrelevant because all educational attainment data is observed long after sample individuals have completed schooling. In our data, a significant proportion of individuals have not completed schooling, allowing us to have meaningful duration effects.}  In order to identify both age and duration effects with our cross-sectional data, we exploit the variation in the year of school closure. Under the assumption that the impact of the policy is not specific to the calendar year of closure, we can estimate Equation \ref{eq:startsLengths} to obtain the impact of the policy as a function of both starting age and the length of exposure.
